---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# antibodySeek
_by **John D. Gagnon**_
<br>
_University of California, San Francisco_

### Table of Contents  
**[Overview](#overview)**<br>
**[Installation](#installation)**<br>
**[Usage](#usage)**<br>
**[Session info](#session-info)**<br>
**[License](#license)**<br>

## Overview

A shinyapp-based GUI to identify available antibodies 

## Installation

1. If you do not already have R installed, or your version is out of date, 
download and install the latest [version](https://cran.r-project.org). 


  + Optionally, install the latest version of 
[RStudio Desktop](https://www.rstudio.com/products/rstudio/#Desktop).


2. Download the package from GitHub

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("jdgagnon/antibodySeek")
```


## Usage

Load the package into the R session.

`library(antibodySeek)`

To initialize the shiny app, paste the following code in your R console 
and run it.

`antibodySeek()`


## Session info

Here is the output of `sessionInfo()` on the system on which this package was
developed:

```{r} 
sessionInfo()
```
<br><br>

## License

[GNU GPL-3.0-or-later](https://www.gnu.org/licenses/gpl.txt)
