---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# antibodySeek
_by **John D. Gagnon**_
<br>
_University of California, San Francisco_

### Table of Contents  
**[Overview](#overview)**<br>
**[Installation](#installation)**<br>
**[Usage](#usage)**<br>
**[Session info](#session-info)**<br>
**[License](#license)**<br>

## Overview

A shinyapp-based GUI to identify available antibodies 

## Installation

1. If you do not already have R installed, or your version is out of date, 
download and install the latest [version](https://cran.r-project.org). 


  + Optionally, install the latest version of 
[RStudio Desktop](https://www.rstudio.com/products/rstudio/#Desktop).


2. Download the package from GitHub

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("jdgagnon/antibodySeek")
```


## Usage

Load the package into the R session.

`library(antibodySeek)`

To initialize the shiny app, paste the following code in your R console 
and run it.

`antibodySeek()`

1. Load a spreadsheet containing the antibody database:

* Spreadsheet must be in the following format:

```{r, echo=FALSE, fig.align='center'}
knitr::kable(
  matrix(c("CD3", "X", "", "",
           "CD4", "", "X", "X",
           "CD8", "X", "X", "X"), 
         ncol = 4, byrow = TRUE), 
  col.names = c("Antibody", "PE", "FITC", "etc..."))
```

* Use the file browser to select a `csv` file 

OR

* Load a spreadsheet from 
`Google Sheets` by filling out the spreadsheet name and clicking 
`Find Google Sheet`. 

* Choose the approprate worksheet

2. Select the antibodies from the dropdown menu that you wish to use.

## Session info

Here is the output of `sessionInfo()` on the system on which this package was
developed:

```{r} 
sessionInfo()
```
<br><br>

## License

[GNU GPL-3.0-or-later](https://www.gnu.org/licenses/gpl.txt)
